\section{Methodology}\vspace{.4cm}
This chapter will focus on the materialized view selection processes, implementation strategies, and best practices for creating and maintaining MV. It will end with highlights of the performance improvements, such as query execution time and scalable systems, that make materialized views important in contemporary database systems.

 \subsection{How Materialized Views Work on MSSQL} Not every database supports materialized views, and those that do each handle them a little differently, especially when it comes to the approach to view maintenance \cite{hattemer-2020}. Microsoft SQL Server supports materialized views. Still, they are called "indexed views" because a materialized view may be indexed in multiple ways, and a materialization step is a matter of creating an index on a regular view. A view is materialized by creating a unique clustered index on an existing view. Uniqueness implies that the view output must contain a unique key. An indexable view must be defined by a single-level SQL statement containing selections, inner joins, and optional group-by \cite{goldstein-2001}.\vspace{0.8cm}

 To create materialized views in MSSQL, a step-by-step creation procedure must be followed:
 \begin{enumerate}
     

     \item\textbf{Identify the query or queries:} The most vital step in materialized view creation is detecting the exact query or queries that will form the view. Hence, they must be fine-tuned to ensure that the required data is fetched optimally and the performance of view generation is optimized. Queries should consider the complexity of determination, the size of their result sets, and the frequency of data updates \cite{castordoc2023}.
     
      \item\textbf{ Write the base query :} Begin by writing the base  SQL query that defines the materialized views. It should contain all necessary data, join, aggregation, or other complex operations that need to be optimized. \vspace{0.4cm}
      \input{SQL/Base_query}
      
      \item\textbf{ Create the materialized view :} After writing the query, proceed to create an indexed view in SQL server using the `` with schemabinding'' clause starting with schema and view name. Schema binding options bind the view to the schema of the underlying tables, preventing changes to the base tables from affecting the view's definition. %\cite*{risingwave2024}.\vspace{0.4cm}

      \input{SQL/MV_on_mssql}

      \item\textbf{ Create a unique clustered index:} This step is very crucial for the SQL server to materialize as it organizes and stores the sorted data of the materialized view based on the indexed column and transforms it into an MV. \vspace{0.4cm}
      
      \input{SQL/Clustered_view} 

This statement materializes the view and stores the result in a clustered index.
      
      \item\textbf{ Configure refresh options:} Finally, it is crucial to refresh the materialized view periodically to ensure it remains up-to-date. This option needs to be configured to decide whether manual, incremental or automatic refreshes will be preferred. Manual refresh is updated at the user's discretion. On the other hand, automatic refresh occurs at scheduled intervals. The frequency of refreshing the materialized view depends on the rate of data updates and the requirements of the application \cite{castordoc2023}. For more details, please refer to the \hyperref[View_maintainance]{\texttt{section}~\ref*{View_maintainance}}.\vspace{0.4cm}
      
      \item\textbf{ Querying the MV:} Once created, configured, and populated, an Mv can be queried just like a table based on cost and necessity.  \vspace{0.4cm}
      

\end{enumerate}

\subsection{Deciding When to Create a Materialized or a Regular View}There are some key factors when designing and optimizing database systems. Two tools that can significantly impact this balance are regular views and materialized views. The following table highlights the key differences between regular views and materialized views, helping to guide the choice between these two approaches based on specific requirements and use cases.\vspace{.4cm}

\input{Table/Regular_vs_MV_View}


 \subsection{Cost Model}
 There is a cost associated with the use of materialized views in database systems. The cost analysis helps in strategic decision-making for designing and maintaining MV, ensuring an optimal balance between performance and cost efficiency. This section will discuss the cost model of Materialized view.\vspace{.4cm}

 \begin{enumerate}[label=\alph*)]
    \item \textbf{Computing cost :} Computing cost mostly depends on the workload and data size. Query processing and data transferring, there are refresh mechanisms to stay accurate. All these procedures are costly. Both the initial creation and subsequent refreshes of materialized views consume compute resources.
    
    \item \textbf{Maintenance cost:} These costs are associated with keeping Materialized views up-to-date and on service as base data changes. Every refresh or recalculation uses compute resources. Regular tuning, indexing, and monitoring to ensure the view optimally benefits query performance. The frequency of updates to base tables and the complexity of the materialized view impact these costs. 
    
    \item \textbf{Storage cost}: Materialized views require additional disk space, particularly for large databases. The gain in query performance should offset the storage cost of MV. Disabled views still incur storage costs, even if they're not maintained or used for query optimization. As data volume grows, the storage costs for MV can increase significantly. This aspect should be considered when designing a long-term strategy for MV. 
     
    \item \textbf{Usage cost:} Materialized views are great to use. However, there is a cost associated with the jobs that maintain them. The cost can be calculated using the following formula\cite{10.1145/2206869.2206874}:

    \input{Math/Total_cost}

  Suppose opta data Group runs a complex query with a materialized view, which takes 1 ms to execute, compared to 5 ms without MV. If it runs 100 times per day, the total savings would be:

  \input{Math/Cost_example}
  
\end{enumerate}

This thesis primarily explores the use of materialized views and the PSO algorithm to improve query performance. It highlights the connection between computing costs and storage costs. Computing costs, which are affected by workload and data size, play a vital role in assessing the PSO algorithm's effectiveness in optimizing query execution plans. On the other hand, storage is also costly as materialized views require additional space, most especially in large databases. The compromise needed between quicker query
execution and growing storage requirements is critical. Through the analysis of these elements, the thesis is to demonstrate how PSO can shift towards better overall query execution by weighing the advantages and disadvantages of materialized views.


\subsection{ Static vs Dynamic View Selection } The selection process for materialized views in query optimization can be classified into static and dynamic. Both alternatives are designed to improve query performance but differ in timing, adaptivity, and resource management. Below is the static and dynamic selection process breakdown:
\begin{enumerate}
        \item \textbf{Static View Selection:} Before executing any query, the process of selecting the static view would involve the materialized views that were selected in the design or setup phase of a database. Whether or not to create and keep particular materialized views is dependent on what has been analyzed historically, workload patterns, and domain knowledge. Views are predefined and fixed until the database reconfiguration is done manually.\vspace{.4cm}
    
    \textbf{Key Characteristics:} In this case, the fixed view predetermines materialized views at the design stage, generally deriving the set predetermined from historical analysis of expected workloads. Once chosen, these remain set unless some manual alteration is applied. This is suitable for the predictable nature of stable workloads where queries are not so prone to changes over time, such as data warehouse environments or environments that perform online analytical processing (OLAP). By saving time spent on choices, static view selection becomes quite easy to implement and run. It has an inherent limitation because any considerable shift in the workload would entail manual intervention in the set of materialized views \cite{lohman2000selftuning,mamoulis2012survey,gupta2002selftuning}.
    \item \textbf{Dynamic View Selection:} Dynamic View Selection is the selection of dynamic materialized views at execution time or the adaptation of a set of materialized views to changing workload patterns. This is thus a continuous process consisting of monitoring query patterns and data modification in conjunction with cost-benefit considerations to decide whether to add a materialized view, maintain one, or remove it.\vspace{.4cm}
    
    \textbf{Key Characteristics:} On the contrary, dynamic view selection automatically identifies, creates, and updates materialized views based on real-time workload analysis. This monitoring method continuously examines the patterns of incoming queries and employs a sophisticated algorithm to determine which views should be created, dropped, or modified. As a result, it is well-suited for environments with unpredictable or rapidly changing workloads, such as transactional databases or mixed workloads that require both operational and analytical capabilities. Its dynamic nature is what makes this technique effective in responding to workload shifts, with the selected materialized views optimized for current usage patterns. However, real-time adaptability comes with implementation complexity and increased maintenance overhead, as it requires ongoing monitoring and decision-making processes. Dynamic view selection involves significant cost trade-offs between maintaining and refreshing views and the benefits gained in processing query performance \cite{lohman2000selftuning,mamoulis2012survey,gupta2002selftuning}.
\end{enumerate}

This paper examines static materialized views, emphasizing their efficiency and simplicity in contexts where the underlying data remains mostly unchanged. By reducing the necessity for constant updates, static views excel in scenarios that prioritize query performance over real-time accuracy. Utilizing static views optimizes query execution and decreases maintenance and storage costs, providing an effective solution for stable datasets.

\subsection{ Materialized View Management and Selection Approach}

A well-structured and systematic selection approach is needed to optimize query performance using materialized views in MSSQL. Below is a detailed overview of the materialized views selection approach for query optimization.

\subsubsection{Materialized View Selection Approach}
  
\begin{enumerate}[label=\alph*)]
    \item \textbf{Query identification:} This is the first step in selecting materialized views to identify which queries are most frequently executed and resource intensive. The prime queries involve a combination of complex joins, aggregation, or large datasets.
    
    \item \textbf{Analyze query patterns:} This step involves analyzing execution logs to determine:
    
     \begin{itemize}
          \item How often specific queries are run.
          \item Resource consumption and average execution time.
          \item The types of operations involved (e.g, joins, aggregations)
      \end{itemize}
      This analysis helps to prioritize which queries should be materialized.
      
    \item \textbf{Storage management:} Access the storage requirements for maintaining materialized views, considering CPU time, I/O operations, and memory usage when determining which materialized views will provide the greatest performance benefit.
    
    \item \textbf{Refresh Policies:} Once queries are identified, design and establish refresh policies based on data volatility or requirements.
\end{enumerate}
\subsubsection{View Matching for Query Optimization }

View matching is an important step in query optimization that determines whether a query or sub-expression can be calculated from existing materialized views. Since the objective of query optimization is to minimize the computational cost of query execution by taking advantage of precomputed results, this is a fundamental component. The view matching typically involves the following steps:\vspace{.4cm}

  \begin{itemize}
      \item \textbf{Query decomposition:} The entering query is reviewed and broken down into its constituent elements, which include projection, selection, aggregation, and joins. This stage aids in determining the information required by the query and the components available in materialized views \cite{theodoratos2000decomposition}.For more details see section ~\ref{Query_decomposition}.

      \item \textbf{Normalization and canonical form:} The incoming input query and the definitions of the materialized views are transformed into a canonical form, facilitating a more straightforward comparison. The normalization aids in removing inconsistency in representing similar operations, allowing it to be more efficient in matching.

     \item \textbf{Checking coverage:} The conditions and attributes of the query are assessed against those present in the materialized view to ascertain if the view encompasses all required data. This procedure guarantees that the materialized view contains all necessary data as specified by the query. When the query includes a WHERE condition, the materialized view must contain an equivalent condition or a more restricted one. See more details in the section ~\ref{Output_checking}.
     
      \item \textbf{Predicate subsumption:} The predicates within the materialized view are evaluated to ascertain whether they subsume the predicates of the incoming query. The selection conditions in the query must be either encompassed by or more stringent than those in the materialized view. If the materialized view's predicates are more general, it remains applicable to the query by implementing further filtering as required \cite{adali1996query}.

      \item \textbf{Query rewriting:} If the materialized view is discovered to encompass the incoming query, the query is subsequently rewritten to utilize the materialized view rather than navigating the basis tables. The rewriting entails restructuring the original query to conform to the schema of the materialized view, usually incorporating extra filters or projections where necessary \cite{haldar2001query}.

         \item \textbf{Cost evaluation:} If there are several materialized views that match the query, the query optimizer computes the cost of using each possible view and picks the one with the lowest estimated cost \cite{hulgeri2001cost}. This stage guarantees the selection of the most efficient execution plan, optimizing aspects such as I/O, memory use, and processing duration. A practical evaluation has been conducted in section ~\ref{Cost_evaluation} with the help of the PSO algorithm.

  \end{itemize}
  

\subsubsection{Conditions that Must be Fulfilled to be Capable of Using Materialized Views:}
To effectively utilize the materialized views, certain conditions must be fulfilled. These ensure that the query optimizer can create, maintain, and effectively use the MV. Here are the key conditions that must be met:

\begin{enumerate}[label=\alph*)]
    \item \textbf{Stable base table:} The underlying table should have a table schema and not experience frequent changes. It can increase the maintenance cost. All columns referenced in the view must belong to base tables.
    
    \item \textbf{Syntax and structural requirements:} The view must be created using the schema binding options to ensure schema consistency. A unique clustered index is mandatory to materialize the view. Insert, update, and delete operations on base tables must not violate the constraints of the view.
    
    \item \textbf{Sufficient storage and permission:} Adequate storage and permission must be available for the user to accommodate the data stored in materialized views.
    
    \item \textbf{Effective refresh Strategies:} A clear strategy for refreshing materialized views is necessary to ensure data accuracy while avoiding excessive maintenance overhead. Further processes are implemented here. For details, see section~\ref{View_maintainance}.
    
    \item \textbf{Assessment:} It is essential to periodically evaluate materialized views (MVs) to keep them accurate and aligned with the evolving needs of database systems. Clear documentation should be maintained for each materialized view, detailing its purpose, structure, and refresh policies. For details, see section~\ref{View_maintainance}.
    
\end{enumerate}

% Three types of materialized views used to increase query performance and reduce response time are as follows:

%%\begin{enumerate}[label=\alph*)]
   % \item \textbf{Materialized view management task}
    %\item \textbf{Materialized view selection}
    %\item \textbf{Incremental Materialized View Maintenance}
%%\end{enumerate}

%\subsubsection{Multiple View Processing Plans }
\subsubsection{Do All Required Rows Exist in the Views }\label{Output_checking}

 The best approach to ensure all required rows exist or to get the expected values without compromising the base table is to use a combination of methods that guarantee accuracy, efficiency, and performance. Here's the best strategy tailored for academic writing:
\begin{enumerate}
    \item \textbf{Row count method} \vspace{.4cm}

    \input{SQL/row_count}
    
Row count comparison confirms that the materialized view holds all required rows. Using the same filter conditions, this step ensures completeness by comparing the total row count of the base table and materialized view. It is suitable for periodic checks under optimization with the advantage of initial verification at minimal computational costs.
    
    \item \textbf{Except method for data completeness} \vspace{.4cm}

    \input{SQL/except_operator}

The query retrieves all data from the base table, and then subtracts all data from the views. If the result is an empty set, it means all rows in the base table exist in MVs. If the result contains rows, those rows are missing from the views. 
    
    \item \textbf{Tertiary Method: CHECKSUM for Data Integrity} \vspace{.4cm}
    
    \input{SQL/checksum}
    
    By comparing the two checksums (\texttt{BaseTable\_Checksum} and \texttt{MV\_Checksum}), this query determines if the data in the materialized view matches the base table. If the checksums differ, it indicates a discrepancy in the data.
\end{enumerate}
 


%\subsubsection{How Particle Swarm Optimization Algorithm Works on MV}
%\subsubsection{Maintenance of Existing Materialized Views }


%\textbf{......\textbf{Work on Progress}..........}       
 
